Notation proposal

### 2011-05-31 notation.tex
fixed interp decimate functions
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@792 ccdd05d5-56c1-461a-bf98-85f6876523b4

Throughout, we will use the convention that $k$ indexes time-series sampled at
the full sample rate $f$ and $k^s$ indexes time-series sampled at a reduced
sample rate $f^s$.  For the case of band limited functions it is sufficient to
simply remove sample points to define the downsampled version as is shown in
the previous equation.

Definition of decimation for a function $f$:
\begin{equation}
f[k^{s+1}] = \sum_{n=-N^\shortdownarrow/2}^{N^\shortdownarrow/2-1} b^\shortdownarrow[n] f\!\left[k^{s} - n\right]
\end{equation}

Definition of interpolation for a function $f$:
\begin{equation}
f[k^{s}] = \sum_{n=-N^\shortuparrow/2}^{N^\shortuparrow/2-1} b^\shortuparrow[n] f\!\left[k^{s+1} - n\right]
\end{equation}

>>>>

Throughout, we will use the convention that $k$ indexes time-series sampled at
the full sample rate $f$ and $k^s$ indexes time-series sampled at a reduced
sample rate $f^s$, ($k^{s} \equiv k f \ f^{s}$).  For the case of band limited
functions it is sufficient to simply remove sample points to define the
downsampled version as is shown in the previous equation.

Definition of decimation for a function $p$:
\begin{equation}
p[k^{s+1}] = \sum_{n=-N^\shortdownarrow/2}^{N^\shortdownarrow/2-1} b^\shortdownarrow[n] \, p\!\left[k^{s}-n\right]
\end{equation}

Definition of interpolation for a function $p$:
\begin{equation}
p[k^{s}] = \sum_{n=-N^\shortuparrow/2}^{N^\shortuparrow/2-1} b^\shortuparrow[n] \, p\!\left[k^{s+1}-n\right]
%p[k^{s}] = \sum_{n=k^{s}-N^\shortuparrow/2}^{k^{s} + N^\shortuparrow/2-1} b^\shortuparrow[k^{s} - n] \, p\!\left[\frac{n f^{s+1}}{f^{s}}\right]
%f[k^{s}] = \sum_{n=-N^\shortuparrow/2}^{N^\shortuparrow/2-1} b^\shortuparrow[n] f\!\left[n \frac{f^{s}}{f^{s+1}}  \right]
\end{equation}
